???Grape Quality and its Link to Regional Differences in the Australian Winegrowing Industry

### 2023-08-29 article.tex
added variable summary table

\subsection{Data}
The Australian wine industry is divided into 65 regions, known as a Geographical Indicator Regions (GI Region). Each GI Region is used to describe different unique localised traits of vineyards across Australia; with each having its own mixture of climatic and geophysical properties \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each region is explicitly defined under the Wine Australia Corporation Act of 1980 \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}. The climatic properties of a GI Region are summarised by Sustainable Winegrowing Australia (2021), where regions of similar climates are amalgamated together into superset regions. The climatic regions were utilised to illustrate similar trends and explain differences between sets of regions.
The data used in this analysis comes from Sustainable Winegrowing Australia and covers the period 2015 to 2022. The dataset contained 3342 samples across 52 GI Regions and 1072 individual vineyards.

>>>>

\subsection{Data}

% 6091 samples - total
% 58 regions
% 10 years

% 853 with reported profits
% 46 regions
% reported since 2018
Data used in this analysis were obtained from Sustainable Winegrowing Australia. Australia's national wine industry sustainability program, which aims to facilitate grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by SWA is entered manually by winegrowers using a web based interface. A total of 6091 observations has been collected over 10 years. Each observation contained 23 variables see Table \ref{tab:vars}.

\begin{table}[]
  \caption{Summary of variables used in the analysis. The recorded column indicate values that were either greater than zero or that were not missing.}\label{tab:summary}
\begin{tabular}{@{}cccc@{}}
  \toprule
  \textbf{} & \textbf{Units} & \textbf{Recorded} & \textbf{\begin{tabular}[c]{@{}c@{}}Number of\\ Classes\end{tabular}} \\ \midrule
  Water Used & Mega Litres & 5846 &  \\
  Diesel & Litres & 5585 &  \\
  Biodiesel & Litres & 25 &  \\
  LPG & Litres & 958 &  \\
  Herbicide Spray & Times per year & 2026 &  \\
  Year & Class & 6091 & 10 \\
  Disease & Class & 6091 & 2 \\
  Region & Class & 6091 & 58 \\
  Solar & Kilowatt Hours & 622 &  \\
  Wind & Kilowatt Hours & 2 &  \\
  Irrigation Type & Class & 6091 & 20 \\
  Petrol & Litres & 4309 &  \\
  Slashing & Times per year & 2290 &  \\
  Yield & Tonnes & 5935 &  \\
  Irrigation Energy & Class & 6091 & 16 \\
  Area Harvested & Hectares & 6091 &  \\
  Electricity & Kilowatt Hours & 1015 &  \\
  Insecticide Spray & Times per year & 1092 &  \\
  Fertiliser & \begin{tabular}[c]{@{}c@{}}Kilograms \\ of Nitrogen\end{tabular} & 795 &  \\
  Fungicide Spray & Times per year & 2260 &  \\
  Cover Crop & Class & 6091 & 32 \\
  Water Type & Class & 6091 & 39 \\
  Profit & AUD & 853 &  \\
  Operating Costs & AUD & 853 &  \\ \bottomrule
  \end{tabular}

 were collected

The data collected pertains to both the physical and

The Australian wine industry is divided into 65 regions, known as a Geographical Indicator Regions (GI Region). Each GI Region is used to describe different unique localised traits of vineyards across Australia; with each having its own mixture of climatic and geophysical properties \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each region is explicitly defined under the Wine Australia Corporation Act of 1980 \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}. The climatic properties of a GI Region are summarised by Sustainable Winegrowing Australia (2021), where regions of similar climates are amalgamated together into superset regions. The climatic regions were utilised to illustrate similar trends and explain differences between sets of regions.
The data used in this analysis comes from Sustainable Winegrowing Australia and covers the period 2015 to 2022. The dataset contained 3342 samples across 52 GI Regions and 1072 individual vineyards.
